Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-08 paper.tex

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). All publishers and all the features have been considered.}
\label{fig:all_publishers_no_fs}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.42]{./imgs/prediction_all_publisher_Table5.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). All publishers and just those features selected by each method have been considered in every case.}
\label{fig:results_all_publishers_fs}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, using all features, with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
% Just the features selected by ReliefFAttributeEval method have been considered.
}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)
% we can discuss this point later this morning.
% The thing is that in this plot we are using all features!! (here, no feature selection method has been used)

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
}
\label{fig:casesReliefFAttributeEval}
\end{figure*}

>>>>

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, including errorbars, with different regression methods (30 repetitions, 10-fold cross validation). All publishers and all the features have been considered.}
%This is not a boxplot - JJ
\label{fig:all_publishers_no_fs}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.42]{./imgs/prediction_all_publisher_Table5.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). All publishers and just those features selected by each method have been considered in every case.}
\label{fig:results_all_publishers_fs}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Barplots showing the values obtained predicting
  \texttt{total\_sales}, using all features, with different regression
  methods (30 repetitions, 10-fold cross validation). Results obtained
  for different special publishing companies: UDL929 (the best selling
  publishing company), UDLW12 (the median selling publishing company),
  UDL704 (highest number of different titles sold) and UDLU11 (medium
  number of different books sold). 
% Just the features selected by ReliefFAttributeEval method have been considered.
}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)
% we can discuss this point later this morning.
% The thing is that in this plot we are using all features!! (here, no feature selection method has been used)

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_ReliefFAttributeEval-FS.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, considering just the features selected by ReliefFAttributeEval method, with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold).
}
\label{fig:casesReliefFAttributeEval}
\end{figure*}
